---
title: "Bake vs Juice"
author: "Paul"
date: '`r format(Sys.Date(), "%d\\. %m\\. %Y")`'
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
options(mc.cores = parallel::detectCores())
library(tidyverse)
theme_set(hrbrthemes::theme_ipsum(base_family = "Arial_Narrow"))
```
# Did Recipe save the function parameter used?

## Simple Data
```{r}
df_train <- data.frame(
  x = 1:3,
  y = 4:6
)

df_test <- data.frame(
  x = 4:6,
  y = 7:9
)
```

## Prepare recipe with training data
```{r}
library(recipes)
```

```{r}
try_rec <- recipes::recipe(
  y ~ x, data = df_train
) %>% 
  step_normalize(all_predictors()) %>% 
  prep()
```

## See the result on test data

```{r}
juice(try_rec)
```
```{r}
bake(try_rec, new_data = df_test)
```
# Perfect!
Recipes does exactly what it is supposed to do!

It used the normalizing parameter fitted from training data onto the normalizing of the testing data!

# What is the difference between using prep or not?

```{r}
try_rec_unpreped <- try_rec %>% 
  step_nzv(x) 
```
```{r}
try_rec_unpreped %>% prep%>% juice
```
```{r}
try_rec_unpreped %>% prep %>% bake(new_data = df_test)

```

# Also see if the response can be standardized well
```{r}
try_rec <- recipes::recipe(
  y ~ x, data = df_train
) %>% 
  step_normalize(all_numeric()) %>% 
  prep()
```

## See the result on test data

```{r}
juice(try_rec)
```
```{r}
bake(try_rec, new_data = df_test)
```
# this also worked!